ms_russia_results

### 2024-10-21 ms-russia-results.Rmd
Add numeric results for Russia consumption changes

rus_of_unfriendly_percent_change <- 100 * ((rus_of_unfriendly_post - rus_of_unfriendly_pre) / rus_of_unfriendly_pre)
```

>>>>

rus_of_unfriendly_percent_change <- 100 * ((rus_of_unfriendly_post - rus_of_unfriendly_pre) / rus_of_unfriendly_pre)

# All consumption
consumption_by_rus_total <- consumption %>%
  filter(consumer_iso3c == "RUS", 
         source_country_iso3c != "RUS",
         ((year %in% 2013:2014) | (year %in% 2015:2016))) %>%
  mutate(period = case_when(
    year %in% 2013:2014 ~ "before_sanctions",
    TRUE ~ "after_sanctions"
  )) %>%
  group_by(period) %>%
  summarise(consumption_live_t = sum(consumption_live_t)) %>%
  ungroup()

rus_of_total_pre <- consumption_by_rus_total %>%
  filter(period == "before_sanctions") %>%
  pull(consumption_live_t)

rus_of_total_post <- consumption_by_rus_total %>%
  filter(period == "after_sanctions") %>%
  pull(consumption_live_t)

rus_total_percent_change <- 100 * ((rus_of_total_post - rus_of_total_pre) / rus_of_total_pre)

# Consumption from friendly countries
consumption_by_rus_friendly <- consumption %>%
  filter(consumer_iso3c == "RUS", 
         source_country_iso3c != "RUS",
         ((year %in% 2015) | (year %in% 2019))) %>%
  mutate(period = case_when(
    year %in% 2015 ~ "at_sanctions",
    TRUE ~ "after_sanctions"
  )) %>%
  group_by(source_sanctions_towards_russia, period) %>%
  summarise(consumption_live_t = sum(consumption_live_t)) %>%
  ungroup()

rus_of_friendly <- consumption_by_rus_friendly %>%
  filter(source_sanctions_towards_russia == "Russia friendly countries")

rus_of_friendly_pre <- rus_of_friendly %>%
  filter(period == "at_sanctions") %>%
  pull(consumption_live_t)

rus_of_friendly_post <- rus_of_friendly %>%
  filter(period == "after_sanctions") %>%
  pull(consumption_live_t)

rus_of_friendly_percent_change <- 100 * ((rus_of_friendly_post - rus_of_friendly_pre) / rus_of_friendly_pre)
```
